\bf Aggregated Financial Forecasting Calculation in Human-Computer Distributed Computing

### 2020-01-12 Aggregated-Financial-Forecasting-Calculation-in-Human-Computer-Distributed-Computing/abstract.tex
Formatting was done.

\author{Petar Tomov, Iliyan Zankinski, Todor Balabanov \textsuperscript{0000-0003-3139-069X} \\ Institute of Information and Communication Technologies \\ Bulgarian Academy of Sciences \\ acad. Georgi Bonchev Str., block 2, office 514, 1113 Sofia, Bulgaria \\ http://www.iict.bas.bg/}

>>>>

\author{Petar Tomov, Iliyan Zankinski, Todor Balabanov\textsuperscript{\tiny 0000-0003-3139-069X} \\ Institute of Information and Communication Technologies \\ Bulgarian Academy of Sciences \\ acad. Georgi Bonchev Str., block 2, 1113 Sofia, Bulgaria \\ http://www.iict.bas.bg/}
